---
title: "Intro to R and Rmarkdown"
author: "David Jackson"
date: "3/8/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(scales)
library(dplyr)
library(forecast)
library(janitor)
library(dlookr)
library(DT)
library(flextable)
library(lubridate)
options(digits = 2)
```

# Level Intro to R, RStudio and Rmarkdown

Error bars are graphical representations of the variability of data and used on graphs to indicate the error or uncertainty in a reported measurement. They give a general idea of how precise a measurement is, or conversely, how far from the reported value the true (error free) value might be.

* List one 


```{r}
rm(list=ls())

df <- read.csv("./StatsServicesExport.csv") %>% remove_empty()
df$SampleDate <- as.Date(df$SampleDate)
df$DateofBirth <- as.Date(df$DateofBirth)
df$USDate <- as.Date(df$USDate)
```

## Create Dicscipive Statistics


```{r}
df %>% select(AgeatEDD:Weight )%>% diagnose_numeric() %>% flextable() 
```

## Count of Smoking/Non and Unknown

```{r}
df$SmokingGroup <- ifelse((df$Smoking =="0"), "No","Unknown")
df$SmokingGroup <- ifelse((df$Smoking =="1"), "Yes",df$SmokingGroup)


smokers <- df %>% group_by(SmokingGroup) %>% summarise(
  Count = n()
) 
```

```{r}
# smokers <- as.data.frame(smokers)
ggplot(smokers) + geom_col(aes(x=SmokingGroup,y=Count)) + scale_y_log10() +
  labs(title="Count of Smoker/non-smoker",y="Total Number of Women(log10)")

```

## Table 1: 1Sample sizes by gestational weeks


```{r}
df$GAweek <-  floor(df$GestationalAge/7) 
table(df$GAweek)
```

## Table 2:  Sample sizes by month and Year

```{r}
df$MY <- format(df$SampleDate, "%Y-%m")
year_month <- as.data.frame( table(df$MY))
ggplot(year_month) + geom_col(aes(x=Var1,y=Freq)) + coord_flip() +
  labs(title="Count of Samples by month and Year",x="Year/Month",y="Count of Samples")

```


## Table 1 Sample sizes by weight groups

```{r}
df$Weight <- floor(df$Weight/10) *10 

table(df$Weight)

```

## Table 1 Ethnic distribution



